Model-based variable selection for regression with highly correlated variables.

### 2014-08-22 www/article.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@818 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\paragraph{Further notations} In the following, we will note also $\boldsymbol{J}_r=(J_{r}^1,\ldots,J_r^{d_r})$ the $d_r$-uple of all the response variable (to be not confused with the corresponding set $J_r$ previously defined), $\boldsymbol{J}_p=(J_{p}^1,\ldots,J_p^{d_r})$ the $d_r$-uple of all the predictors for all the sub-regressions, $\boldsymbol{d}_p=(d_p^1,\ldots,d_p^{d_{r}})$ the associated number of predictors and $\boldsymbol{S}=(\boldsymbol{J}_r,\boldsymbol{J}_p)$ the global {\it model} of all the sub-regressions. As more compact notations, we define also $\boldsymbol{X}_r=\boldsymbol{X}^{J_{r}}$ the whole set of response covariates and also $\boldsymbol{X}_f=\boldsymbol{X}^{J_{f}}$ the {\it all} other covariates, denominating now as {\it free} covariates, including these ones used as predictor covariates in $\boldsymbol{J}_p$ or not. An illustration of all these notations is displayed through an example in Section~\ref{sec:tradeoff}. The parameters are also stacked together: $\boldsymbol{\alpha}=(\boldsymbol{\alpha}_1,\ldots,\boldsymbol{\alpha}_{d_r})$ denotes the global coefficient of sub-regressions and $\boldsymbol{\sigma}^2=(\boldsymbol{\sigma}^2_1,\ldots,\boldsymbol{\sigma}^2_{d_r})$ denotes the corresponding global variance.

\paragraph{Remarks}
\begin{itemize}
\item Sub-regressions defined in (\ref{eq:SR}) are very easy to understand by any practitioner and, thus, will give a clear view of all the correlations present in the dataset at hand.
\item As a consequence of Hypothesis~\ref{H1}, ``free'' covariates $\boldsymbol{X}_f$ are {\it all} decorrelated.
\item We have considered correlations between the covariates of the main regression on $\boldsymbol{Y}$, not between the residuals. Thus $\boldsymbol{S}$ does not depend on $\boldsymbol{Y}$ and it can be estimated independently as we will see in Section~\ref{sec:estimateS}.
\item The model of sub-regressions $\boldsymbol{S}$ gives a system of linear regressions that can be viewed as a recursive Simultaneous Equation Model (\textsc{sem})\cite{davidson1993estimation,TIMM} or also as a Seemingly Unrelated Regression (\textsc{sur}) \cite{SURzellner}. 
\end{itemize}

@@

\begin{hyp}\label{H4}
All variates $\boldsymbol{X}^j\in\boldsymbol{X}_f$ are mutually independent and arise from the following Gaussian mixture of $k_j$ components
\begin{equation}
\mathbb{P}(\boldsymbol{X}_f^j|\boldsymbol{S};\boldsymbol{\pi}_{j},\boldsymbol{\mu}_j,\boldsymbol{\lambda}^2_j) = \sum_{h=1}^{k_j} \pi_{hj} \mathcal{N}_n(\mu_{hj} . (1,\ldots,1)',\lambda_{hj}^2\boldsymbol{I}),
\end{equation}
where $\boldsymbol{\pi}_{j}=(\pi_{1j},\ldots,\pi_{k_jj})$ is the vector of mixing proportions with $\pi_{hj}>0$ and $\sum_{h=1}^{k_j}\pi_{hj}=1$, $\boldsymbol{\mu}_j=(\mu_{1j},\ldots,\mu_{k_jj})$  is the vector of centers and $\boldsymbol{\lambda}^2_j=(\lambda^2_{1j},\ldots,\lambda^2_{k_jj})$ is the vector of variances. We stack together all the mixture parameters in $\boldsymbol{\theta}=(\boldsymbol{\pi}_{j},\boldsymbol{\mu}_j,\boldsymbol{\lambda}^2_j ; j \in J_f)$.
\end{hyp}

>>>>

\paragraph{Further notations} In the following, we will note also $\boldsymbol{J}_r=(J_{r}^1,\ldots,J_r^{d_r})$ the $d_r$-uple of all the response variable (to be not confused with the corresponding set $J_r$ previously defined), $\boldsymbol{J}_p=(J_{p}^1,\ldots,J_p^{d_r})$ the $d_r$-uple of all the predictors for all the sub-regressions, $\boldsymbol{d}_p=(d_p^1,\ldots,d_p^{d_{r}})$ the associated number of predictors and $\boldsymbol{S}=(\boldsymbol{J}_r,\boldsymbol{J}_p)$ the global {\it model} of all the sub-regressions. As more compact notations, we define also $\boldsymbol{X}_r=\boldsymbol{X}^{J_{r}}$ the whole set of response covariates and also $\boldsymbol{X}_f=\boldsymbol{X}^{J_{f}}$ the {\it all} other covariates, denominating now as {\it free} covariates, including these ones used as predictor covariates in $\boldsymbol{J}_p$ or not. An illustration of all these notations is displayed through an example in Section~\ref{sec:tradeoff}. The parameters are also stacked together: $\boldsymbol{\alpha}=(\boldsymbol{\alpha}_1,\ldots,\boldsymbol{\alpha}_{d_r})$ denotes the global coefficient of sub-regressions and $\boldsymbol{\sigma}^2=(\sigma^2_1,\ldots,\sigma^2_{d_r})$ denotes the corresponding global variance.

\paragraph{Remarks}
\begin{itemize}
\item Sub-regressions defined in (\ref{eq:SR}) are very easy to understand by any practitioner and, thus, will give a clear view of all the correlations present in the dataset at hand.
\item As a consequence of Hypothesis~\ref{H1} and~\ref{H2} , ``free'' covariates $\boldsymbol{X}_f$ are {\it all} decorrelated.
\item We have considered correlations between the covariates of the main regression on $\boldsymbol{Y}$, not between the residuals. Thus $\boldsymbol{S}$ does not depend on $\boldsymbol{Y}$ and it can be estimated independently as we will see in Section~\ref{sec:estimateS}.
\item The model of sub-regressions $\boldsymbol{S}$ gives a system of linear regressions that can be viewed as a recursive Simultaneous Equation Model (\textsc{sem})\cite{davidson1993estimation,TIMM} or also as a Seemingly Unrelated Regression (\textsc{sur}) \cite{SURzellner}. 
\end{itemize}

@@

\begin{hyp}\label{H4}
All variates $\boldsymbol{X}^j$ with $j \in J_f$ are mutually independent and arise from the following Gaussian mixture of $k_j$ components
\begin{equation}
\mathbb{P}(\boldsymbol{X}_f^j|\boldsymbol{S};\boldsymbol{\pi}_{j},\boldsymbol{\mu}_j,\boldsymbol{\lambda}^2_j) = \sum_{h=1}^{k_j} \pi_{hj} \mathcal{N}_n(\mu_{hj} . (1,\ldots,1)',\lambda_{hj}^2\boldsymbol{I}),
\end{equation}
where $\boldsymbol{\pi}_{j}=(\pi_{1j},\ldots,\pi_{k_jj})$ is the vector of mixing proportions with $\forall 1\leq h\leq k_j , \pi_{hj}>0$ and $\sum_{h=1}^{k_j}\pi_{hj}=1$, $\boldsymbol{\mu}_j=(\mu_{1j},\ldots,\mu_{k_jj})$  is the vector of centers and $\boldsymbol{\lambda}^2_j=(\lambda^2_{1j},\ldots,\lambda^2_{k_jj})$ is the vector of variances. We stack together all the mixture parameters in $\boldsymbol{\theta}=(\boldsymbol{\pi}_{j},\boldsymbol{\mu}_j,\boldsymbol{\lambda}^2_j ; j \in J_f)$.
\end{hyp}
